Improved Approximation Algorithms for the Maximum Carpool Matching Problem

### 2017-02-06 src/sub.tex
fix

Buchbinder et al.~\cite{BFNS15} presented a general randomized
$2$-approximation algorithm for unconstrained submodular maximization.

@@

\begin{figure}
\centering
\input{fig-submodular}
\caption[]{
\label{fig:defs}
In this example, $M$ is the set of the blue, dashed arcs, then:
$val_M(2) = 7$,
$val_M(3) = 2$,
$val_M(6) = 0$,
$\delta_M(2, 3) = 1$,
$\delta_M(6, 3) = 2$,
the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
$\text{pass}_M(2) = \{1, 4\}$.
}
\end{figure}

>>>>

Buchbinder et al.~\cite{BFNS15,buchbinder2016deterministic} presented a
general randomized $2$-approximation algorithm for unconstrained submodular maximization.

@@

\begin{figure}
\centering
\input{fig-submodular}
\caption[]{
\label{fig:defs}
We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
redistributed over \subref{sub:s} and \subref{sub:s} \todo{write explanation}}
\end{figure}
